Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-07-07 ms.tex
I got rid of multiply defined references to the pupil fraction table.
I changed the reference for the DHS versus no DHS posteriors from the histograms to now the corner plot since they're updated.

One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:DHSposterios}.
A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.

@@

\begin{table}
\centering
\begin{tabular}{cc}
DHS \# & Pupil Fraction \\
\hline \hline
1 & 0.012 \\
2 & 0.032 \\
3 &  0.032 \\
4 & 0.040 \\
5 & 0.021 \\
6 & 0.015 \\
7 & 0.042 \\
8 & 0.040 \\
9 & 0.036 \\
10 & 0.022 \\
\hline
Total & 0.292
\end{tabular}
\caption{Pupil Coverage}\label{tab:pupfrac}
\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}\label{tab:pupfrac}
\end{table}

>>>>

One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances, seen in Figure \ref{fig:cornerRun}.
A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor.
However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}.
Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.

@@

\begin{table}
\centering
\begin{tabular}{cc}
DHS \# & Pupil Fraction \\
\hline \hline
1 & 0.012 \\
2 & 0.032 \\
3 &  0.032 \\
4 & 0.040 \\
5 & 0.021 \\
6 & 0.015 \\
7 & 0.042 \\
8 & 0.040 \\
9 & 0.036 \\
10 & 0.022 \\
\hline
Total & 0.292
\end{tabular}
\caption{Pupil Coverage}\label{tab:pupfrac}
\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
\end{table}
